\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{url}
\usepackage{color}
\usepackage{array}
\usepackage{multirow}
%\usepackage{subfigure}

%%%%%%%%%% verbatim related
\usepackage{fancyvrb}
\usepackage{fixltx2e}
\fvset{framesep=2mm,fontsize=\scriptsize,framerule=.1mm,numbersep=1mm,commandchars=\\\{\}}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}


%%%%%%%%%%%%%%%%%%

\newcommand{\eat}[1]{}
\newcommand{\rmv}[1]{ #1}
\newcommand{\sysname}{XXXXXX}

\newif\ifrev
% comment out the following line after the revision is done
\revtrue
\ifrev
  \newcommand{\cappos}[1]{{\color{red} [Justin: #1]}}
  \newcommand{\reznik}[1]{{\color{blue} [Leon: #1]}}
  \newcommand{\weiss}[1]{{\color{green} [Richard: #1]}}
 \newcommand{\yanyan}[1]{{\color{blue} [Yanyan: #1]}}
\else
  \newcommand{\cappos}[1]{}
  \newcommand{\reznik}[1]{}
  \newcommand{\weiss}[1]{}
\fi

\begin{document}

\title{Trust Evaluation in Mobile Devices: \\An Empirical Study}
%\author{Richard Weiss$^{\star}$, Leon Reznik$^*$, Yanyan Zhuang$^{\dag, \ddag}$, Andrew Hoffman$^*$\\
%Albert Rafetseder$^{\dag}$, Tao Li$^{\dag}$, Justin Cappos$^{\dag}$, \\
%$^{\star}$Evergreen College, $^*$Rochester Institute of Technology\\
%$^{\dag}$New York University, $^{\ddag}$University of British Columbia}

\author{\IEEEauthorblockN{Richard Weiss}
\IEEEauthorblockA{Evergreen College\\
Olympia, WA, USA\\
Email: weissr@evergreen.edu\\
{ }}\\
\IEEEauthorblockN{Andrew Hoffman}
\IEEEauthorblockA{Department of Computer Science\\
Rochester Institute of Technology\\
Rochester, NY, USA\\
Email: arh4555@rit.edu}\\
\IEEEauthorblockN{Tao Li}
\IEEEauthorblockA{Computer Science and Engineering\\
New York University\\
New York, NY, USA\\
Email: litao.alex@gmail.com}
\and

\IEEEauthorblockN{Leon Reznik}
\IEEEauthorblockA{Department of Computer Science\\
Rochester Institute of Technology\\
Rochester, NY, USA\\
Email: lr@cs.rit.edu}\\
\IEEEauthorblockN{Darrell Pollard}
\IEEEauthorblockA{Department of Computer Science\\
Rochester Institute of Technology\\
Rochester, NY, USA\\
Email: dap2525@rit.edu}
\and

\IEEEauthorblockN{Yanyan Zhuang}
\IEEEauthorblockA{Computer Science and Engineering\\
New York University\\
New York, NY, USA\\
Email: yyzh@nyu.edu}\\
\IEEEauthorblockN{Albert Rafetseder}
\IEEEauthorblockA{Computer Science and Engineering\\
New York University\\
New York, NY, USA\\
Email: albert.rafetseder@univie.ac.at}\\
\IEEEauthorblockN{Justin Cappos}
\IEEEauthorblockA{Computer Science and Engineering\\
New York University\\
New York, NY, USA\\
Email: jcappos@nyu.edu}
}

\maketitle

  
\begin{abstract}
A network of mobile systems is both complex and diverse.  This paper presents a
framework to evaluate the trustworthiness of the individual components in a mobile system, as well as the entire system. 
The major components are applications, devices and networks of devices.  
Given this diversity and multiple levels of a mobile system, we develop
a hierarchical trust evaluation methodology, which enables the combination of trust metrics 
and allows us to verify the trust metric for each component
based on the trust metrics for others.

The paper first demonstrates this idea for individual applications and Android-based smartphones.
The methodology involves two stages: initial trust evaluation and trust verification.
In the first stage, an expert rule system is used to produce trust metrics at the lowest level of
the hierarchy.  In the second stage, the trust metrics are verified
by comparing data from components and a trust evaluation is produced for the 
combined system.  This paper presents the results of two empirical studies, in which 
this methodology is applied and tested. The first study involves 
monitoring resource utilization and evaluating trust based on 
resource consumption patterns. We measured battery voltage, CPU utilization and network communication
for individual apps and detected anomalous behavior that could be indicative of malicious code.
The second study involves verification of the trust evaluation by 
comparing the data coming from two different devices: the 
GPS location information from an Android smartphone traveling in an automobile and the data from the speedometer
sensor of the same vehicle.
% which can be used to decrease the trust evaluation of the smartphone if they are inconsistent.

%Smartphones  are rich in sensors and network easily with other mobile devices and wearable computers.

\eat{
  Smartphones and mobile devices install software from a 
wide range of sources.  As these devices become
more popular, the risks of associated malware will become more significant.
One of the features of these platforms is that they are rich in
sensors\footnote{In this work, smartphone sensors are broadly defined as hardware components that can record phenomena about the physical world.}.  These sensors can be a risk to privacy in that they could leak information about the 
user and user activities.  On the other side, they can also be used as an
advantage if they can be used to evaluate trust.
%leak information about any malware that is running on it.  
This paper builds  a hierarchical trust evaluation 
 framework 
that uses sensors to evaluate trust and detect anomalies.

The paper describes the hierarchical trust evaluation framework 
developed and tested for Android based smartphones.  
} % end comment


%Sensor values like battery level 
%and CPU utilization can detect this.  The second study uses a comparison of erroneous sensor values
%from the GPS sensor on a smartphone with speed data from the OBD port on an automobile.
%These are examples in which malware could produce an intentional or inadvertant effect on sensors, such 
%ass GPS receivers or a speedometer, and could be detected by measuring anomalies 
%in these sensor values. 

\eat{
Our approach is two-fold: evaluating trust based on metrics 
and models, \yanyan{more specific what the metrics and models are?} and 
using this evaluation to detect anomalies as a way to improve security in general.} % end comment

\eat{For many people, smartphones and other mobile devices serve as a technical interface to the modern world.
These smart devices have embedded on-board sensors, such as accelerometers, gyroscopes, GPS sensors, and
cameras, which are very useful.

This work describes \sysname, a hierarchical framework for checking consistency of sensors 
from multiple devices.  In addition, it relies on Blursense, a dynamic, fine-grained, flexible access
control mechanism, acting as a line of defense that allows users to define and addprivacy filters. 
As a result, the user can expose filtered sensor data to untrusted apps, and researchers can collect 
data in a way that safeguards users' privacy.}  %end comment
\end{abstract}

%\IEEEpeerreviewmaketitle

\input{intro} % this will describe the problem and applications, threat models
\input{umbrella} % summary of section 2 of the Hoffman paper
\input{iHeartRadio}  % what is anomalous behavior, how are resources monitored?
\input{blursense}
  % description of the experiments: comparisons of driving data
\input{OBD} % summary of sensibility platform with some blursense added and
            %  description of the OBD system
%\input{results}  
\input{conclusion}

\section*{Acknowledgement}
This work was partially supported by NSF grants 1141341, 0834243, 
1223588, 1205415, 1241568, and an NYU-AIG (American International Group)
grant.

% \section*{Acknowledgment}
% Weiss was supported by the National Science Foundation through grant TUES-1141341 
% Cappos was supported by the National Science Foundation through grants 
\bibliographystyle{ieeetr}
%\bibliographystyle{abbrv}
\bibliography{bibdata,trust}

\end{document}

